Manuscript drafts

### 2020-03-11 manuscript/drafts/manuscript.Rmd
- update meeting notes

- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
- justification - 
- background 
- guidance to reader 
- summary/conclusion
---
This study is about how machine learning algorithms can increase efficiency in systematic reviews. I will write about what SRs are, and how workload can be reduced.

>>>>

- objectives - to demonstrate effectiveness of ml algorithm in reducing abstract classification for systematic reviews 
- justification 
- background 
- guidance to reader 
- summary/conclusion

-----

This study is about how machine learning algorithms can increase efficiency in systematic reviews. I will write about what SRs are, and how workload can be reduced.
